### 2015-12-02 paper.tex
More comments in figure captions re turbine orientation

    \caption{{\bf Mean Velocity.}Mean velocity field (looking upstream) at 1 m
    downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and $\lambda=3.1$. Refer to
    Fig.~\ref{fig:coordinates} for turbine axis orientation.}

@@

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/k_contours}
\caption{{\bf Turbulence Kinetic Energy.}
Turbulence kinetic energy at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
$\lambda=3.1$.}
\label{fig:kcont}
\end{figure}

>>>>

    \caption{{\bf Mean Velocity.} Mean velocity field (looking upstream) at 1 m
    downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and $\lambda=3.1$. Refer to
    Fig.~\ref{fig:coordinates} for turbine axis orientation. Solid dark gray
    lines indicate turbine frontal area.}

@@

\begin{figure}[h]
    \includegraphics[width=\textwidth]{figures/k_contours}

    \caption{{\bf Turbulence Kinetic Energy.} Turbulence kinetic energy (looking
    upstream) at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
    $\lambda=3.1$. Solid black lines indicate turbine frontal area.}

    \label{fig:kcont}
\end{figure}
